### 2015-01-25 src/paper4/p4_discussion.tex
Updated paper 4

[Introduction]

Discuss how VOR scaling relates to our results!

We compared the parameter for the near condition, , found in the present paper to the one we previously found in a similar experiment where we compared body-fixed to world-fixed fixations at near (50 cm) distances only. Figure 6 shows how well our model explains the data in our previous paper, the positive correlation between the actual PSEs and those predicted using the model in this paper (stats) adds confidence to the parameter values for  presented here. The average difference between the values found here and those reported previously (see Table 2) is 12 ±8 percent-points, indicating a variation of about 12\% on the contribution of the vestibular system vs that of the visual system between the present and our previous paper. While the variation might seem high, keep in mind that the two parameter values presented in this study are fitted on only four conditions, which do not overlap with the two conditions used to fit  parameter  previously.
There are two possible explanations for our results, first the weight could be a function of fixation depth; second it could be that eye movements are used to modulate self-motion perception.

If the eye movement weight was a function of fixation depth, and the oculomotor and vestibular signals are combined in a statistically optimal fashion, the vestibular weight would we weighted more with increasing fixation depth. As there is no effect in the body condition, we can rule out that fixation depth is taken into account in a statistically optimal fashion.

Should eye movements influence self-motion perception, then we would expect no effects in the body near versus body far condition because of the absence of eye movements in this condition. As the eye movements in the world near interval are smaller than those in equidistant world far intervals, we would expect underestimation of self-motion in the world far condition when compared to the world near condition. Note that it is possible that some compensation for the effects of depth on the eye movements is present, but as long as such compensation is incomplete effects between the world fixed condtions are still to be expected.

>>>>

We investigated whether the eye movements used in self-motion perception \cite{clemens2015a} are properly scaled by fixation distance, as required by the geometry. Experiments assessed self-motion perception during either body- and world-centered fixation at two different fixation depths. During far world-centered fixation (where eye movements are small) self-motion was underestimated compared to nearby world-centered fixation (where eye movements are large). Fixation depth did not influence self-motion perception during body-centered fixation (where eye movements are absent). To quantify the relative depth-dependent scaling of eye movements for nearby and far away fixation targets, we fitted a simple linear model to the perceptual and oculomotor responses across four conditions. While two participants show partial scaling, the six remaining participant did not show any sign of scaling.

In addition to the absence of scaling, another explanation is that eye movement information is integrated in a statistically optimal fashion, taking signal noise into account. In the world-fixed condition, this would mean that noisy eye movements in the far fixation are weighed less than those in the less noisy ones in the near fixation condition, giving rise to the observed difference. In this case, similar optimal integration should also occur in the body-fixed fixation condition. As no such differences between the near and far body-fixed fixation conditions have been observed, this is unlikely to be the case.

As it becomes impossible to distinguish between body- and world-fixed fixation point at far fixation distances, the lack of scaling could - in theory - be explained by participants incorrectly perceiving both the body- and world-fixed far fixation points as being body-fixed. This is unlikely because the target displacement associated with a world-fixed target was between X and Y degrees in our experiment, which is easily perceivable especially given that the target was foveated. This adds confidence to our hypothesis that eye movements indeed influence self-motion perception, with moderate to no scaling for fixation depth.

% Relation to Clemens, 2015
\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/paper4/paper4_figure6.eps}

    \caption{...}
    \label{p4:fig6}
\end{figure}

In our previous experiment we compared body-fixed to world-fixed fixations at near (50 \si{\centi\metre}) distances only \cite{clemens2015a}. We compared the parameter, $\alpha$, found in that paper with the parameters for the near condition, $\alpha_{50}$, found in the present study. \figref{p4:fig6} shows how well our $\alpha_{50}$ parameter explains the data in our previous paper, the positive correlation between the actual PSEs and those predicted using the model in this paper (stats) adds confidence to the parameter values for  presented here. The average difference between the values found here and those reported previously (see \tabref{p4:tab2}) is 12 \textpm 8 percent-points, indicating a variation of about 12\% on the contribution of the vestibular system versus that of the visual system between the present and our previous paper. While the variation might seem high, keep in mind that the two parameter values presented in this study are fitted on only four conditions, which do not overlap with the two conditions used to fit  parameter  previously.

% Relation to the VOR, e.g. Paige and Busettini
Because the LVOR is commonly thought to keep the eyes stable during linear translation (reference), it also needs to scale with fixation depth. It is therefore possible that both the LVOR and self-motion perception use the same signal. While the fixation point in our experiment causes optokinetically driven eye movements to suplement the LVOR compensation, it is known that the LVOR only partially compensates for the amount of linear translation. If the same signal is also used for self-motion perception, one would expect that, the ratio of the expected LVOR compensation at 50 and 200cm reflect the ones presented in this paper (see \figref{p4:fig5} and \tabref{p4:tab2}).

It has been shown that the relative amount of compensation, or gain, depends on fixation distance angle \cite{paige1989, busettini1994,paige1998}. When fixating far away the gain is closer to 1 compared to fixations closer by. We extrapolated the gains found by Paige, 1989 to the 50 and 200cm fixation distances in our experiment and found gains of 0.50 and 0.68 respectively.

The expected LVOR compensation based on these gains is 5.6 and 3.0 degrees for near and far fixation respectively. The ratio, 1.87, does not match either the 6 participants who do not show any sign of scaling ($\frac{d_{200}}{d_{50}} = 1.07 \pm 0.16$) or the 2 that do ($\frac{d_{200}}{d_{50}} = 3.06 \pm 0.27$), but does match the overall overage of  1.56 \textpm 0.35.

### 2015-01-25 src/paper4/p4_intro.tex
Updated paper 4

When the eyes track world-centered objects, their angular displacement is directly related to the size of the motion. Therefore, we recently proposed that these tracking eye movements could also be used as a self-motion cue, in addition to optic flow and vestibular signals. To test this hypothesis, we compared self-motion perception in the absence of full-field optic flow during passively induced whole-body translations (Clemens et al., 2015). Supporting this notion, our results showed that self-motion is underestimated during body-centered fixations (in which the eyes remain stationary in their orbits) compared to when world-centered fixations (in which the eyes must move to maintain fixation).

@@

In the present study, we investigate how fixation distance influences perception of self-motion across passive lateral translation. Using a psychophysical approach, participants had to indicate whether the second body displacement of two one-second translation intervals was smaller or longer than the first. We show that translation amplitude is perceived smaller when fixating a far rather than a nearby world-centered target, indicating that eye movements are not properly scaled for self-motion perception. Together with the further observation that self-motion perception with body-centered fixation targets is not affected by fixation depth, we conclude that eye movements are merely a rudimentary cue to self-motion, with a compensation for fixation depth that is partical at best.

>>>>

When the eyes track world-centered objects, their angular displacement is directly related to the size of the motion. Therefore, we recently proposed that these tracking eye movements could also be used as a self-motion cue, in addition to optic flow and vestibular signals. To test this hypothesis, we compared self-motion perception in the absence of full-field optic flow during passively induced whole-body translations \cite{clemens2015a}. Supporting this notion, our results showed that self-motion is underestimated during body-centered fixations (in which the eyes remain stationary in their orbits) compared to when world-centered fixations (in which the eyes must move to maintain fixation).

@@

In the present study, we investigate how fixation distance influences perception of self-motion across passive lateral translation. Using a psychophysical approach, participants had to indicate whether the second body displacement of two one-second translation intervals was smaller or longer than the first. We show that translation amplitude is perceived smaller when fixating a far rather than a nearby world-centered target, indicating that eye movements are not properly scaled for self-motion perception. Together with the further observation that self-motion perception with body-centered fixation targets is not affected by fixation depth, we conclude that eye movements are merely a rudimentary cue to self-motion, with a compensation for fixation depth that is partial at best.

### 2015-01-25 src/paper4/p4_methods.tex
Updated paper 4

Eight naïve participants (three male, five female), aged between 22 and 29 years, gave written informed consent to participate in the study. They were all free of any known vestibular or neurological disorder and had normal or corrected-to-normal visual acuity. Participants never received any feedback about their performance. The present study was part of a larger study on the effects of eye movements on self-motion perception, some of the results of which were described in our recent report \cite{clemens2015a}. Details about the setup and methods have been described extensively in that report as well. Here we provide only a brief summary.

@@

We fit \eqnref{p4:eq5} to the data using linear regression, finding one weight for every fixation depth (that is, $\alpha_{50}$ and $\alpha_{200}$) that minimizes the sum of squared errors ($\Sigma \epsilon^2$). Because these parameters can, in theory, contain both a depth dependent and a depth independent scaling, we compute their ratio, $\frac{\alpha_{50}}{\alpha_{200}}$, to remove any depth independent components. In case of perfect compensation, the expected ratio is $\frac{50}{200} = \frac{1}{4}$, while in case of no depth-dependent scaling it is 1.

>>>>

Eight na\"ive participants (three male, five female), aged between 22 and 29 years, gave written informed consent to participate in the study. They were all free of any known vestibular or neurological disorder and had normal or corrected-to-normal visual acuity. Participants never received any feedback about their performance. The present study was part of a larger study on the effects of eye movements on self-motion perception, some of the results of which were described in our recent report \cite{clemens2015a}. Details about the setup and methods have been described extensively in that report as well. Here we provide only a brief summary.

@@

We fit \eqnref{p4:eq5} to the data using linear regression, finding one weight for every fixation depth (that is, $\alpha_{50}$ and $\alpha_{200}$) that minimizes the sum of squared errors ($\Sigma \epsilon^2$). Because these parameters can, in theory, contain both a depth dependent and a depth independent scaling, we compute their ratio, $\frac{\alpha_{50}}{\alpha_{200}}$, to remove any depth independent components. In case of perfect compensation, the expected ratio is $\frac{50}{200} = 1/4$, while in case of no depth-dependent scaling it is 1.

### 2015-01-25 src/paper4/p4_results.tex
Updated paper 4

\begin{table}
    \begin{tabular}{l|lll}
	Participant & $\alpha_{50}$ & $\alpha_{200}$ & $\alpha$ \\
    \hline
	1 & 0.37 & 0.25 & 0.27 \\
	2 & 0.51 & 0.41 & 0.27 \\
	3 & 0.36 & 0.30 & 0.35 \\
	4 & 0.14 & 0.29 & 0.06 \\
	5 & 0.11 & 0.04 & 0.13 \\
	6 & 0.49 & 0.15 & 0.33 \\
	7 & 0.40 & 0.53 & 0.58 \\
	8 & 0.42 & 0.35 & 0.21 \\
    \end{tabular}

    \caption{.}

@@

%%%%

As the weighing parameters encompassed both depth dependent as well as depth independent effects, it is possible to remove the depth independent effects by taking the ratio between the two parameters. The ratio between  and  is plotted per participant in Figure 5. In case there is no depth compensation, i.e. when , the expected ratio is one. Perfect compensation, that is when , the expected ratio is 4. While two participants show moderate compensation for depth, the majority of participants show no sign of such compensation.

>>>>

\begin{table}
    \begin{tabular}{l|lll|l}
	Participant & $\alpha_{50}$ & $\alpha_{200}$ & $\frac{d_{200}}{d_{50}}$ & $\alpha$ \\
    \hline
	1 & 0.37 & 0.25 & 1.46 & 0.27 \\
	2 & 0.51 & 0.41 & 1.25 & 0.27 \\
	3 & 0.36 & 0.30 & 1.22 & 0.35 \\
	4 & 0.14 & 0.29 & 0.49 & 0.06 \\
	5 & 0.11 & 0.04 & 2.79 & 0.13 \\
	6 & 0.49 & 0.15 & 3.34 & 0.33\\
	7 & 0.40 & 0.53 & 0.76 & 0.58 \\
	8 & 0.42 & 0.35 & 1.25 & 0.21 \\
    \end{tabular}

    \caption{Best-fit parameter values for 50 and 200 \si{\centi\metre} fixation distances, $\alpha_{50}$ and $\alpha_{200}$ respectively (see \eqnref{p4:eq5}), and their ratio, $\frac{\alpha_{200}}{\alpha_{50}} = \frac{d_{200}}{d_{50}}$, for each participant. Best-fit parameter values, $\alpha$, from our previous paper \protect\cite{clemens2015a} are included for reference.}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{src/paper4/paper4_figure5.eps}

	\caption{}
	\label{p4:fig5}
\end{figure}

By taking the ratio of these weighting parameters, any depth independent effects were removed. As this ratio contains only depth dependent effects, it is equal to the ratio of depths used for eye movement scaling. In case there is no depth scaling, i.e. when $d_{50} = d_{200}$, the expected ratio is one. Perfect compensation, that is when $d_{50} = 50  \wedge d_{200} = 200$, the expected ratio is $1/4$. The actual ratio between $d_{50}$ and $d_{20}$ is plotted for each participant in \figref{p4:fig5}. While two participants show moderate compensation for depth, the majority of participants show no sign of scaling of eye movements by fixation distance. This is consistent with the observation in the world condition that translations are perceived shorter with far compared to near fixations.
